\Large \textbf{Cooperation Is Provably Required for Success in a Version of the Noisy Iterated Prisoner's Dilemma}

### 2020-05-22 paper/paper.tex
first draft

  We are now finally ready to prove that to be evolutionarily stable, a strategy needs to cooperate with a clone of itself.

@@

      The underlying idea is to construct $s_2$ such that $s_1$ can see no difference between itself and $s_2$, while $s_2$, on the other hand, can. If we succeed in doing so, we will have that $v_{s_1}(s_2) = v_{s_2}(s_1) = v_{s_1}(s_1)$, and can construct $s_2$ such that it always cooperates when it recognizes itself, thereby yielding $v_{s_2}(s_2) = R$. This would give $s_2$ a higher fitness than $s_1$. The rest of this proof executes this plan in detail.

@@

      We now construct a $K_H$ for each $H$. \Cref{c2flowchart} shows the high-level construction of $K_H$.
       All of the steps succeed with probability $1 - O(p)$. The first step makes sure that $K_H$ does not deviate from $s_1$ at all
        until $s_1$ has reached an absorbing strongly connected component. 
       Once $s_1$ is in an absorbing strongly connected component, it cannot escape, and $s_2$ can also force it to end up in any of the states in the component, which means that even if $s_1$ after this point ``figures out'' that it is not playing against itself anymore, there's nothing it can do about it.
      The second step in the construction of $K_H$ makes sure that if $s_2$ is playing against itself, it is in sync with its clone; that is, with probability $1 - O(p)$, both copies of $s_2$ will transition to the third component at the exact same time (although not necessarily in the same $K_H$). 
      The third step now figures out what action $s_1$ would take at some large finite time $T$. 
      Then, $K_H$ outputs the exact opposite action at time $T$. 
      At that point, if its opponent outputs $s_1$'s expected action, it wants to transition into the absorbing strongly connected component $H_\text{copy}$, which is just an exact copy of $H$, but if its opponent outputs the opposite of that action, it has successfully recognized itself and enters an always cooperating state.
      Before transitioning into $H_\text{copy}$, $s_2$ makes sure that $s_1$ is in a state that is beneficial for $s_2$.

      \begin{figure}
        \centering
        \begin{tikzpicture}[node distance=0.9cm,initial text=]
          \node[elliptic state, initial, initial where=above] (c_0) {1. Wait until $s_1$ is in an absorbing SCC, while simulating $H$.};
          \node[elliptic state] (c_1) [below=of c_0] {2. Sync $s_2$.};
          \node[elliptic state] (c_3) [below=of c_1] {3. Figure out what action that $s_1$ will take right after this.};
          \node[state] (c_4) [below left=of c_3] {$C$};
          \node[state] (c_5) [below right=of c_3] {$D$};
          \node[state] (c_6) [below=of c_5] {$C$};
          \node[elliptic state] (c_7) [below=of c_4] {4. Force $s_1$ into a good state.};
          \node[elliptic state] (c_8) [below=of c_7] {$H_\text{copy}$ \\(an exact copy of $H$)};

          \path[->] (c_0) edge (c_1);
          \path[->] (c_1) edge (c_3);
          \path[->] (c_3) edge node [above left] {$s_1$ will take $D$} (c_4);
          \path[->] (c_3) edge node [above right] {$s_1$ will take $C$} (c_5);
          \path[->] (c_4) edge node [below, pos=0.1] {$C$} (c_6);
          \path[->] (c_5) edge node [right] {$D$} (c_6);
          \path[->] (c_4) edge node [left] {$D$} (c_7);
          \path[->] (c_5) edge node [below, pos=0.1] {$C$} (c_7);
          \path[->] (c_6) edge [loop right] (c_6);
          \path[->] (c_7) edge (c_8);
          % \path[->] (c_0) edge node [above right] {$\bar{\alpha}$} (c_1);
          % \path[->] (c_1) edge [loop right] node [right] {$C,D$} ();
          % \path[->] (c_0) edge node [above left] {$\alpha$} (c_prime);
          % \path[->] (c) edge node [below left] {$\alpha$} (c_prime);
        \end{tikzpicture}
        \caption{High level construction of $K_H$, the absorbing component replacing $H$ when creating $s_2$ in the proof of \cref{evolutionarystable1}. Note that $K_H$ contains exactly 2 absorbing strongly connected components. SCC means strongly connected component.}
        \label{c2flowchart}
      \end{figure}

      This concludes the high-level construction of $s_2$. We now want to prove that this $s_2$ can in fact invade $s_1$. To do that, we will first assume that the below four lemmas are correct, i.e., that the construction is possible and works as specified, and then finish the proof of our theorem using those assumptions. Once that's done, we will prove the four lemmas.

@@

      \begin{lemma}
        \label{claimpayoffs}
        Given the above construction of $s_2$, the payoffs are as follows.
      \begin{align*}
        v_{s_1}(s_1) &= \gamma \pm O(p), \\
        v_{s_2}(s_2) &= R \pm O(p),
      \end{align*}
      and either
      \begin{align*}
        \lim_{p \to 0} v_{s_2}(s_1) > \gamma,
      \end{align*}
      or
      \begin{align*}
        v_{s_1}(s_2) = \gamma \pm O(p) \text{ and }
        v_{s_2}(s_1) = \gamma \pm O(p).
      \end{align*}
      \end{lemma}
      \begin{subproof}
        By our definition of $\gamma$, we have that $v_{s_1}(s_1) \leq \gamma \pm O(p)$.

@@

        Consider now the case of $s_1$ playing against $s_2$. Suppose that $s_2$ ends up in the absorbing component $K_H$. By \cref{claimcanwaitfors1}, with probability $1 - O(p)$, $s_2$ is indistinguishable from $s_1$ until $s_1$ reaches an absorbing strongly connected component, which we call $H'$.         
        This means that the probability of reaching the absorbing component $H' \times K_H$ in the $s_1$-$s_2$ Markov chain, is up to a factor of $1 - O(p)$ the same as if we had not replaced $H$ by $K_H$ in $s_2$, which is just the probability of reaching the absorbing component $H' \times H$ in the $s_1$-$s_1$ Markov chain. Thus, 
        \begin{equation*}
          P(\text{$s_1$-$s_2$ ends up in $H' \times K_H$}) = (1 - O(p)) P(\text{$s_1$-$s_1$ ends up in $H' \times H$})
        \end{equation*}
        Now, by \cref{claimcanfigureout}, the probability that $s_2$ enters the absorbing strongly connected component $H_\text{copy}$ after having gotten to $K_H$ is $1 - O(p)$ when playing against $s_1$. Thus,
        \begin{equation}
          \label{equationhhcopy}
          P(\text{$s_1$-$s_2$ ends up in $H' \times H_\text{copy}$}) = P(\text{$s_1$-$s_1$ ends up in $H' \times H$}) \pm O(p).
        \end{equation}
        % Let $C_H$ be the always cooperating absorbing state of $K_H$. Then, this equation implies that 
        % \begin{equation}
        %   \label{equationhch}
        %   P(\text{$s_1$-$s_2$ ends up in $H' \times C_H$}) = O(p).
        % \end{equation}
        By \cref{claimcanforcegoodstate}, $s_1$ can choose to end up in any absorbing strongly connected component $S_{H', H}$ that is a subset of $H' \times H_\text{copy}$, with probability $1 - O(p)$. 
        Naturally, $s_1$ chooses an $S_{H', H}^*$ as follows: among the $S$ that have the maximum payoff for $s_2$, not caring about $O(p)$, we choose the one the minimizes the payoff for $s_1$.
        Let $v_{s}(S)$ denote the payoff that strategy $s$ achieves in the absorbing strongly connected component $S$. Then,
        \begin{equation}
          \label{imtoootired}
          v_{s_2}(S_{H', H}^*) \geq \sum_{S} P(\text{$s_1$-$s_1$ ends up in $S$} \mid \text{$s_1$-$s_1$ ends up in $H' \times H$}) \cdot v_{s_1}(S) \pm O(p)
        \end{equation}
        since the right hand side is a weighted average of $v_{s_1}(S)$, which is the same as $v_{s_2}(S)$ in this case, which is what we maximized over when we chose $S_{H', H}^*$. Also, since $s_1$ could make sure to get into it with probability $1 - O(p)$, we have 
        \begin{equation}
          \label{eqshh}
          P(\text{$s_1$-$s_2$ ends up in $S_{H',H}^*$}) = P(\text{$s_1$-$s_2$ ends up in $H' \times H_\text{copy}$})  \pm O(p).
        \end{equation}
        Also, as a consequence, the $S_{H,H'}^*$ for all $H$ and $H'$ become the only absorbing strongly connected components with probabilities of ending up in them greater than $O(p)$.

@@

        \begin{align*}
          \WithArrowsOptions{displaystyle}
          \begin{WithArrows}
          v_{s_2}(s_1) &= \sum_{S \in \mathcal{B}} P(\text{$s_1$-$s_2$ ends up in $S$}) \cdot v_{s_2}(S) \\
          &= \sum_{S_{H',H}^*} P(\text{$s_1$-$s_2$ ends up in $S_{H', H}^*$}) \cdot v_{s_2}(S_{H', H}^*) \pm O(p) \Arrow{\cref{eqshh}} \\
          &= \sum_{S_{H',H}^*} P(\text{$s_1$-$s_2$ ends up in $H' \times H_\text{copy}$}) \cdot v_{s_2}(S_{H', H}^*) \pm O(p) \Arrow{\cref{equationhhcopy}} \\
          &= \sum_{S_{H',H}^*} P(\text{$s_1$-$s_1$ ends up in $H' \times H$}) \cdot v_{s_2}(S_{H', H}^*) \pm O(p) \Arrow{\cref{imtoootired}}\\
          &\geq \sum_{S \in \mathcal{A}} P(\text{$s_1$-$s_1$ ends up in $S$}) \cdot v_{s_1}(S) \pm O(p)\\
          &= v_{s_1}(s_1) \pm O(p)
          \end{WithArrows}
        \end{align*}
        Thus, we have that $v_{s_2}(s_1) \geq \gamma \pm O(p)$. Suppose that $v_{s_2}(s_1) = \gamma \pm O(p)$. Then, we must have equality in \cref{imtoootired} for all $H$ and $H'$, which means that all $S$ were equally good for $s_2$, in which case we chose $S_{H',H}^*$ to minimize the payoff for $s_1$. Following through with the exact same argument as above, but flipping the inequalities, we then find that $v_{s_1}(s_2) \leq \gamma \pm O(p)$.

      \end{subproof}

      Given \cref{claimpayoffs}, we simply compute $F(s_2) - F(s_1)$, which we want to show is greater than 0. We have two cases. First, we assume that $\lim_{p \to 0} v_{s_2}(s_1) > \gamma$. Let $\lim_{p \to 0} v_{s_2}(s_1) = \beta$. Then,
      \begin{align*}
        F(s_2) - F(s_1) &= \\
        &= (1 - \epsilon) \cdot v_{s_2}(s_1) + \epsilon \cdot v_{s_2}(s_2) - (1 - \epsilon) \cdot v_{s_1}(s_1) - \epsilon \cdot v_{s_1}(s_2) \\
        &= (1 - \epsilon) (\beta \pm O(p)) + \epsilon (R \pm O(p)) - (1-\epsilon) (\gamma \pm O(p)) - \epsilon (v_{s_1}(s_2) \pm O(p)) \\
        &\geq (1 - \epsilon) (\beta - \gamma) + \epsilon(R - v_{s_1}(s_2)) \pm O(p)
      \end{align*}
      Here, we can make $\epsilon$ small enough such that this becomes positive, since $\beta - \gamma > 0$. Now, in the second case, we assume that $v_{s_2}(s_1) = \gamma \pm O(p)$ and $v_{s_1}(s_2) \leq \gamma \pm O(p)$. Then,
      \begin{align*}
        F(s_2) - F(s_1) &= \\
        &= (1 - \epsilon) \cdot v_{s_2}(s_1) + \epsilon \cdot v_{s_2}(s_2) - (1 - \epsilon) \cdot v_{s_1}(s_1) - \epsilon \cdot v_{s_1}(s_2) \\
        &\geq (1 - \epsilon) (\gamma \pm O(p)) + \epsilon (R \pm O(p)) - (1-\epsilon) (\gamma \pm O(p)) - \epsilon (\gamma \pm O(p)) \\
        &\geq \epsilon (R - \gamma) \pm O(p)
      \end{align*}
      We know that $R - \gamma > 0$ by our initial assumption. Here, we can make $p$ small enough such that this becomes positive.

      In conclusion, our constructed $s_2$ has higher fitness than $s_1$. This proves that $s_2$ can invade $s_1$, and thus, that $s_1$ is not $\epsilon$-invadable some value of $p < p_0$ and some $\epsilon < \epsilon_0$. In conclusion, then, $s_1$ is not evolutionarily stable, which concludes the proof of \cref{evolutionarystable1}.

@@

      We now return to the three lemmas that we left out, which detail the construction of $s_2$.

@@

        Let $T_1$ be the random variable designating the time at which $s_1$ transitions into an absorbing strongly connected component, counting from the time $s_2$ entered $K_H$. (In particular, if $s_1$ is already in an absorbing strongly connected component, $T_1 = 0$.)
        Let $T_2$ be the random variable designating the time at which $s_2$ transitions out of component 1 of $K_H$.
        To prove our lemma, we want to prove that with probability $1 - O(p)$, $T_1 \leq T_2$, and that during all the time that we are in component 1 of $K_H$, the output of $s_2$ is indistinguishable from $H$.

        First, we deal with the indistinguishableness part. We create the component by copying $H$. Next, we define a new graph $W$, that we will design in the subsequent paragraphs, which will wait for $s_1$ to get into an absorbing component. This graph will have edges defined with the labels $C$ and $D$ still, but have no outputs at the states. The graph $D$ will also have one designated ``end state.'' We will then construct our component 1 for $K_H$ by replacing every state $h \in H$ with a copy of $D$ that we call $D_h$. There will be a $C$ edge from node $u \in D_h$ to node $v \in D_{h'}$ if and only if there is a $C$ edge from $h$ to $h'$, and from $u$ to $v$ in $D$. Similarly for the $D$ edge. This is commonly known as the Kronecker or tensor product of the graphs $D$ and $H$. The output at every state $u \in D_h$ is the same as the output of $h$. For the end state $e \in D_h$ for each $h$, we will add an edge with label both $C$ and $D$, transitioning out of this component and into component 2.

        It is clear that as long as we don't transition out of this component, the Kronecker product will ensure that the output will be indistinguishable from $H$. We now want to design $D$ such that $T_1 \leq T_2$ with high probability.

        Let $d$ be the maximum length of a path from any state in $s_1$ to its closest absorbing strongly connected component. Then, for each state in $s_1$, there is a sequence of perceived inputs of length $\leq d$ (the \textit{special sequence} of that state), such that $s_1$ upon seeing that sequence ends up in an absorbing strongly connected component. For all states, the probability that $s_1$ 
        perceives its special sequence is $\geq p^d$, since, in the worst case, $s_1$ would need to make a mistake on exactly all 
        inputs to perceive the special sequence. That means that at any single point in time, there is a probability $\geq p^d$ that $s_1$ 
        will go into an absorbing strongly connected component within the subsequent $d$ moves. Consider the geometric random variable $X_1 = d + \operatorname{Geom} (p^d)$. For all $t$, then, we have that $P(X_1 = t) \leq P(T_1 = t)$. Thus, we may see $X_1$ as some sort of upper bound to $T_1$.
4
        We now describe the construction of $D$. Consider a state $c_1 \in s_1$ and a state $h \in H$, and suppose that we let them evolve with no mistakes happening at all. Then, the outputs of $c_1$ will form an infinite string $w(c_1, h)$. Let there be $|s_1|$ states in $s_1$ and $|H|$ states in $H$. Now, create a string $w^*$ of length $|s_1| \cdot |H|$, which differs in at least 1 place from each $w(c_1,h)$.\footnote{This is the famous technique of diagonalization.} Thus, if $s_1$ ever outputs the string $w^*$ when we are in this component, we know that at least one mistake has occurred, somewhere. Consequently, the probability that, at each timestep, $w^*$ will be perceived by $s_2$ as the next sequence of outputs of $s_1$ is $\leq p$. 
        If we repeat $w^*$ $d+1$ times to form $(w^*)^{d+1}$, the probability that that string is perceived by $s_2$ as the next sequence of outputs of $s_1$ is $\leq p^{d+1}$.
        Now, create $D$ as follows: it is a chain of states $d_1,d_2,\ldots,d_{(d+1)|w^*|+1}$ where $d_i$ transitions to $d_{i+1}$ on seeing the $i$th character of the string $(w^*)^{d+1}$; $d_i$ transitions to $d_1$ otherwise. $d_{(d+1)|w^*|+1}$ is the designated end state of $D$. Now, it is clear that each step, the probability that we will reach the end state in the next $(d+1)|w^*|+1$ steps is $\leq p^{d+1}$. Consider the geometric random variable $X_2 = (d+1)|w^*| + 1 + \operatorname{Geom} (p^{d+1})$. For all $t$, then, we have that $P(X_2 = t) \geq P(T_2 = t)$. Thus, we may see $X_2$ as a lower bound to $T_2$.

@@

      \begin{proof}[Proof of \cref{claimcansyncs2}]
        This construction is relatively simple. It is a chain of states where each state transitions to the next on both input $C$ and $D$ (that is, deterministically). Let $w_H^*$ be the string used in the proof of \cref{claimcanwaitfors1} for component $H$. Let $W = \sum_{H} (d+1) | w_H^* |$. Then, the outputs of the first $W$ states form the string $w_H^*$ repeated $d+1$ times, for all $w_H$. The following $W+1$ states always output $D$. This is followed by one last state outputting $C$. The $C$ state has a transition into itself on input $D$, and out of this component (to component 3 of $K_H$) on input $C$.

>>>>

In this subsection, we prove that evolutionary stability requires that a strategy be cooperating with a clone of itself.

@@

      The underlying idea is to construct $s_2$ such that $s_1$ can see no difference between itself and $s_2$, while $s_2$, on the other hand, can. If we succeed in doing so, we will have that $v_{s_1}(s_2) = v_{s_2}(s_1) = v_{s_1}(s_1)$, and will be able to construct $s_2$ such that it always cooperates when it recognizes itself, thereby yielding $v_{s_2}(s_2) = R$. This would give $s_2$ a higher fitness than $s_1$. The rest of this proof executes this plan in detail.

@@

      We now describe how to construct $K_H$ for each $H$. \Cref{c2flowchart} shows the high-level construction of $K_H$.
       All of the steps succeed with probability $1 - O(p)$. The first step makes sure that $K_H$ does not deviate from $s_1$ at all
        until $s_1$ has reached an absorbing strongly connected component. 
       Once $s_1$ is in an absorbing strongly connected component, it cannot escape, and $s_2$ can also force it to end up in any of the states in the component, which means that even if $s_1$ after this point ``figures out'' that it is not playing against itself anymore, there's nothing it can do about it.
      The second step in the construction of $K_H$ makes sure that if $s_2$ is playing against itself, it is in sync with its clone; that is, with probability $1 - O(p)$, both copies of $s_2$ will transition to the third component at the exact same time (although not necessarily in the same $K_H$). 
      The third step figures out what action $s_1$ would take at some large finite time $T$. 
      Then, $K_H$ outputs the exact opposite action at time $T$. 
      At that point, if its opponent outputs $s_1$'s expected action, it wants to transition into the absorbing strongly connected component $H_\text{copy}$, which is just an exact copy of $H$, but if its opponent outputs the opposite of that action, it has successfully recognized itself and thus enters an always cooperating state.
      Before transitioning into $H_\text{copy}$, $s_2$ makes sure that $s_1$ is in a state that is beneficial for $s_2$.

      \begin{figure}
        \centering
        \begin{tikzpicture}[node distance=0.9cm,initial text=]
          \node[elliptic state, initial, initial where=above] (c_0) {1. Wait until $s_1$ is in an absorbing SCC, while simulating $H$.};
          \node[elliptic state] (c_1) [below=of c_0] {2. Sync up with $s_2$.};
          \node[elliptic state] (c_3) [below=of c_1] {3. Figure out what action that $s_1$ will take right after this.};
          \node[state] (c_4) [below left=of c_3] {$C$};
          \node[state] (c_5) [below right=of c_3] {$D$};
          \node[state] (c_6) [below=of c_5] {$C$};
          \node[elliptic state] (c_7) [below=of c_4] {4. Force $s_1$ into a good state.};
          \node[elliptic state] (c_8) [below=of c_7] {$H_\text{copy}$ \\(an exact copy of $H$)};

          \path[->] (c_0) edge (c_1);
          \path[->] (c_1) edge (c_3);
          \path[->] (c_3) edge node [above left] {$s_1$ will take $D$} (c_4);
          \path[->] (c_3) edge node [above right] {$s_1$ will take $C$} (c_5);
          \path[->] (c_4) edge node [below, pos=0.1] {$C$} (c_6);
          \path[->] (c_5) edge node [right] {$D$} (c_6);
          \path[->] (c_4) edge node [left] {$D$} (c_7);
          \path[->] (c_5) edge node [below, pos=0.1] {$C$} (c_7);
          \path[->] (c_6) edge [loop right] (c_6);
          \path[->] (c_7) edge (c_8);
          % \path[->] (c_0) edge node [above right] {$\bar{\alpha}$} (c_1);
          % \path[->] (c_1) edge [loop right] node [right] {$C,D$} ();
          % \path[->] (c_0) edge node [above left] {$\alpha$} (c_prime);
          % \path[->] (c) edge node [below left] {$\alpha$} (c_prime);
        \end{tikzpicture}
        \caption{High-level construction of $K_H$, the absorbing component replacing $H$ in the creation of $s_2$ in the proof of \cref{evolutionarystable1}. Note that $K_H$ contains exactly 2 absorbing strongly connected components. SCC is short for strongly connected component.}
        \label{c2flowchart}
      \end{figure}

      This concludes the high-level construction of $s_2$. We now want to prove that this $s_2$ can in fact invade $s_1$. To do that, we will first assume that the below four lemmas are correct, that is, that the construction is possible and works as specified, and then finish the proof of our theorem using those assumptions. Once that's done, we will prove the four lemmas.

@@

      \begin{lemma}
        \label{claimpayoffs}
        Given the above construction of $s_2$, the payoffs are as follows.
      \begin{align*}
        v_{s_1}(s_1) &= \gamma \pm O(p), \\
        v_{s_2}(s_2) &= R \pm O(p),
      \end{align*}
      and either
      \begin{align*}
        \lim_{p \to 0} v_{s_2}(s_1) > \gamma,
      \end{align*}
      or
      \begin{align*}
        v_{s_2}(s_1) = \gamma \pm O(p) \text{ and }
        v_{s_1}(s_2) \leq \gamma \pm O(p).
      \end{align*}
      \end{lemma}
      \begin{subproof}
        By our definition of $\gamma$, we have that $v_{s_1}(s_1) = \gamma \pm O(p)$.

@@

        Consider now the case of $s_1$ playing against $s_2$. Suppose that $s_2$ ends up in the absorbing component $K_H$. By \cref{claimcanwaitfors1}, with probability $1 - O(p)$, $s_2$ is indistinguishable from $s_1$ until $s_1$ reaches an absorbing strongly connected component, which we call $H'$.         
        This means that the probability of reaching the absorbing component $H' \times K_H$ of the $s_1$-$s_2$ Markov chain, is up to a factor of $1 - O(p)$ the same as if we had not replaced $H$ by $K_H$ in $s_2$, which is just the probability of reaching the absorbing component $H' \times H$ in the $s_1$-$s_1$ Markov chain. Thus, 
        \begin{equation*}
          P(\text{$s_1$-$s_2$ ends up in $H' \times K_H$}) = (1 - O(p)) P(\text{$s_1$-$s_1$ ends up in $H' \times H$})
        \end{equation*}
        Now, by \cref{claimcanfigureout}, the probability that $s_2$ enters the absorbing strongly connected component $H_\text{copy}$ after having gotten to $K_H$ is $1 - O(p)$ when playing against $s_1$. Thus,
        \begin{equation}
          \label{equationhhcopy}
          P(\text{$s_1$-$s_2$ ends up in $H' \times H_\text{copy}$}) = P(\text{$s_1$-$s_1$ ends up in $H' \times H$}) \pm O(p).
        \end{equation}
        % Let $C_H$ be the always cooperating absorbing state of $K_H$. Then, this equation implies that 
        % \begin{equation}
        %   \label{equationhch}
        %   P(\text{$s_1$-$s_2$ ends up in $H' \times C_H$}) = O(p).
        % \end{equation}
        By \cref{claimcanforcegoodstate}, $s_1$ can choose to end up in any absorbing strongly connected component $S_{H', H}$ that is a subset of $H' \times H_\text{copy}$, with probability $1 - O(p)$. 
        Naturally, $s_1$ chooses an $S_{H', H}^*$ as follows: among the $S$ that have the maximum payoff for $s_2$, in the limit as $p$ goes to 0, we choose the one the minimizes the payoff for $s_1$.
        Let $v_{s}(S)$ denote the payoff that strategy $s$ achieves in the absorbing strongly connected component $S$ of the Markov chain. Then,
        \begin{equation}
          \label{imtoootired}
          v_{s_2}(S_{H', H}^*) \geq \sum_{S} P(\text{$s_1$-$s_1$ ends up in $S$} \mid \text{$s_1$-$s_1$ ends up in $H' \times H$}) \cdot v_{s_1}(S) \pm O(p)
        \end{equation}
        since the right hand side is a weighted average of $v_{s_1}(S)$, which is the same as $v_{s_2}(S)$ in this case, which is what we maximized over when we chose $S_{H', H}^*$. Also, since $s_2$ could ensure with probability $1 - O(p)$ that the Markov chain enters $S_{H',H}^*$ (by \cref{claimcanforcegoodstate}), we have
        \begin{equation}
          \label{eqshh}
          P(\text{$s_1$-$s_2$ ends up in $S_{H',H}^*$}) = P(\text{$s_1$-$s_2$ ends up in $H' \times H_\text{copy}$})  \pm O(p).
        \end{equation}
        Also, as a consequence, the collection of $S_{H,H'}^*$ for all $H$ and $H'$ become the only absorbing strongly connected components with probabilities of ending up in them greater than $O(p)$.

@@

        \begin{align*}
          \WithArrowsOptions{displaystyle}
          \begin{WithArrows}
          v_{s_2}(s_1) &= \sum_{S \in \mathcal{B}} P(\text{$s_1$-$s_2$ ends up in $S$}) \cdot v_{s_2}(S) \\
          &= \sum_{S_{H',H}^*} P(\text{$s_1$-$s_2$ ends up in $S_{H', H}^*$}) \cdot v_{s_2}(S_{H', H}^*) \pm O(p) \Arrow{\cref{eqshh}} \\
          &= \sum_{S_{H',H}^*} P(\text{$s_1$-$s_2$ ends up in $H' \times H_\text{copy}$}) \cdot v_{s_2}(S_{H', H}^*) \pm O(p) \Arrow{\cref{equationhhcopy}} \\
          &= \sum_{S_{H',H}^*} P(\text{$s_1$-$s_1$ ends up in $H' \times H$}) \cdot v_{s_2}(S_{H', H}^*) \pm O(p) \Arrow{\cref{imtoootired}}\\
          &\geq \sum_{S \in \mathcal{A}} P(\text{$s_1$-$s_1$ ends up in $S$}) \cdot v_{s_1}(S) \pm O(p)\\
          &= v_{s_1}(s_1) \pm O(p)
          \end{WithArrows}
        \end{align*}
        Thus, we have that $v_{s_2}(s_1) \geq \gamma \pm O(p)$. Suppose that $v_{s_2}(s_1) = \gamma \pm O(p)$. Then, we must have equality in \cref{imtoootired} for all $H$ and $H'$, which means that all $S$ were equally good for $s_2$, in which case we chose $S_{H',H}^*$ to minimize the payoff for $s_1$. Following through with the exact same argument as above, but flipping the inequalities, we then find that $v_{s_1}(s_2) \leq \gamma \pm O(p)$. This proves the lemma.
      \end{subproof}

      Given \cref{claimpayoffs}, we simply compute $F(s_2) - F(s_1)$, which we want to show is greater than 0. We have two cases. First, we assume that $\lim_{p \to 0} v_{s_2}(s_1) > \gamma$. Let $\lim_{p \to 0} v_{s_2}(s_1) = \beta$. Then,
      \begin{align*}
        F(s_2) - F(s_1) &= \\
        &= (1 - \epsilon) \cdot v_{s_2}(s_1) + \epsilon \cdot v_{s_2}(s_2) - (1 - \epsilon) \cdot v_{s_1}(s_1) - \epsilon \cdot v_{s_1}(s_2) \\
        &= (1 - \epsilon) (\beta \pm O(p)) + \epsilon (R \pm O(p)) - (1-\epsilon) (\gamma \pm O(p)) - \epsilon (v_{s_1}(s_2) \pm O(p)) \\
        &= (1 - \epsilon) (\beta - \gamma) + \epsilon(R - v_{s_1}(s_2)) \pm O(p)
      \end{align*}
      Here, we can make $\epsilon$ and $p$ small enough such that this becomes positive, since $\beta - \gamma > 0$. Now, in the second case, we assume that $v_{s_2}(s_1) = \gamma \pm O(p)$ and $v_{s_1}(s_2) \leq \gamma \pm O(p)$. Then,
      \begin{align*}
        F(s_2) - F(s_1) &= \\
        &= (1 - \epsilon) \cdot v_{s_2}(s_1) + \epsilon \cdot v_{s_2}(s_2) - (1 - \epsilon) \cdot v_{s_1}(s_1) - \epsilon \cdot v_{s_1}(s_2) \\
        &\geq (1 - \epsilon) (\gamma \pm O(p)) + \epsilon (R \pm O(p)) - (1-\epsilon) (\gamma \pm O(p)) - \epsilon (\gamma \pm O(p)) \\
        &\geq \epsilon (R - \gamma) \pm O(p)
      \end{align*}
      We know that $R - \gamma > 0$ by our initial assumption. Here, we can make $p$ small enough such that this becomes positive.

      In conclusion, our constructed $s_2$ has higher fitness than $s_1$. This proves that $s_2$ can invade $s_1$, and thus, that $s_1$ is $\epsilon$-invadable some values of $p < p_0$ and some $\epsilon < \epsilon_0$. In conclusion, then, $s_1$ is not evolutionarily stable, which concludes the proof of \cref{evolutionarystable1}.

@@

      We now return to the four lemmas that we left out, which detail the construction of $s_2$.

@@

        Let $T_1$ be a random variable designating the time at which $s_1$ transitions into an absorbing strongly connected component, counting from the time that $s_2$ entered $K_H$. (In particular, if $s_1$ is already in an absorbing strongly connected component, $T_1 = 0$.)
        Let $T_2$ be a random variable designating the time at which $s_2$ transitions out of component 1 in $K_H$.
        To prove our lemma, we want to prove that with probability $1 - O(p)$, $T_1 \leq T_2$, and that during all the time that we are in component 1 of $K_H$, the output of $s_2$ is indistinguishable from $H$.

        First, we deal with the indistinguishability part. We create the component by copying $H$. Next, we define a new graph $W$, that we will design in the subsequent paragraphs, which will wait for $s_1$ to get into an absorbing component. This graph will have edges defined with the labels $C$ and $D$, but will have no outputs at its states. The graph $W$ will also have one designated end state. We will then construct our component 1 for $K_H$ by replacing every state $h \in H$ with a copy of $W$ that we call $W_h$. There will be a $C$ edge from node $u \in W_h$ to node $v \in W_{h'}$ if and only if there is a $C$ edge from $h$ to $h'$ in $H$, and from $u$ to $v$ in $W$. Similarly for the $D$ edge. This is commonly known as the Kronecker or tensor product of the graphs $H$ and $W$. The output at every state $u \in W_h$ is the same as the output of $h$. For the end state $e \in W_h$ for each $h$, we will add an edge labeled both $C$ and $D$, transitioning out of this component and into component 2.

        It is clear that as long as we don't transition out of this component, the Kronecker product will ensure that the output will be indistinguishable from $H$. We now want to design $W$ such that $T_1 \leq T_2$ with high probability.

        Let $d$ be the maximum length of a path from any state in $s_1$ to its closest absorbing strongly connected component. Then, for each state in $s_1$, there is a sequence of perceived inputs of length $\leq d$ (the \textit{special sequence} for that state), such that $s_1$ upon seeing that sequence ends up in an absorbing strongly connected component. For all states, the probability that $s_1$ 
        perceives its special sequence is $\geq p^d$, since, in the worst case, $s_1$ would need to make a mistake on exactly all 
        inputs to perceive the special sequence. That means that at any single point in time, there is a probability $\geq p^d$ that $s_1$ 
        will go into an absorbing strongly connected component within the subsequent $d$ moves. Consider the geometric random variable $X_1 = d + \operatorname{Geom} (p^d)$. We may see $X_1$ as some sort of upper bound to $T_1$.

        We now describe the construction of $W$. Consider a state $c_1 \in s_1$ and a state $h \in H$, and suppose that we let them evolve with no mistakes happening at all. Then, the outputs of $s_1$ will form an infinite string $l(c_1, h)$. Let there be $|s_1|$ states in $s_1$ and $|H|$ states in $H$. Now, create a string $l^*$ of length $|s_1| \cdot |H|$, which differs in at least 1 place from each $l(c_1,h)$.\footnote{This is the famous technique of diagonalization.} Thus, if $s_1$ ever outputs the string $l^*$ when we are in this component, we know that at least one mistake has occurred, somewhere. Consequently, the probability that, at each timestep, $l^*$ will be perceived by $s_2$ as the next sequence of outputs of $s_1$ is $\leq p$. 
        If we repeat $l^*$ for $d+1$ times to form $(l^*)^{d+1}$, the probability that that string is perceived by $s_2$ as the next sequence of outputs of $s_1$ is $\leq p^{d+1}$.
        Now, create $W$ as follows: it is a chain of states $w_1,w_2,\ldots,w_{(d+1)|l^*|+1}$ where $w_i$ transitions to $w_{i+1}$ on seeing the $i$th character of the string $(l^*)^{d+1}$; $w_i$ transitions to $w_1$ otherwise. $w_{(d+1)|l^*|+1}$ is the designated end state of $W$. Now, it is clear that each step, the probability that we will reach the end state in the next $(d+1)|l^*|+1$ steps is $\leq p^{d+1}$. Consider the geometric random variable $X_2 = (d+1)|l^*| + 1 + \operatorname{Geom} (p^{d+1})$. We may see $X_2$ as a lower bound to $T_2$.

@@

      \begin{proof}[Proof of \cref{claimcansyncs2}]
        This construction is relatively simple. It is a chain of states where each state transitions to the next on both input $C$ and $D$ (that is, deterministically). Let $l_H^*$ be the string used in the proof of \cref{claimcanwaitfors1} for component $H$. Let $L = \sum_{H} (d+1) | l_H^* |$. Then, the outputs of the first $L$ states form the string $l_H^*$ repeated $d+1$ times, for all $l_H$. The following $L+1$ states always output $D$. This is followed by one last state outputting $C$. The $C$ state has a transition into itself on input $D$, and out of this component (to component 3 of $K_H$) on input $C$.

        Suppose that $s_2$ plays against a clone $s_2'$ of itself, and that $s_2$ enters an absorbing component $K_H$ first. Then, by \cref{claimcanwaitfors1}, using the fact that $s_2'$ is a copy of $s_1$ before it reaches an absorbing component, $s_2$ will not enter component 2 of $K_H$ until $s_2'$ enters an absorbing component $K_{H'}$, with probability $1 - O(p)$. When $s_2$ enters component 2, it will at some point output the entirety of the string $l_{H'}^*$. With probability $1 - O(p)$, $s_2'$ will then, by our construction of component 1, enter component 2. That is, $s_2'$ enters the first part of component 2 before $s_2$ leaves the first part of component 2, which means that $s_2$ is at most $L$ steps ahead of $s_2$. This means that $s_2'$ will be in the defection part of the chain when $s_2$ reaches the cooperation state. Assuming no mistakes, then, $s_2$ will wait until $s_2'$ also reaches the cooperation state, at which point they will both simultaneously leave the component. This happens with probability $1 - O(p)$, as desired.
      \end{proof}
